Vision Paper: Efficient Spatio-Temporal Geo-Statistics for Exploratory Data Analysis

### 2018-05-24 Workshop_GIScience_BigData_Vision.tex
paper name changed

A framework for evacuation hotspot detection after large scale disasters using location data from smartphones: case study of Kumamoto earthquake \cite {Yabe:2016:FEH:2996913.2997014}

>>>>

A framework for evacuation hotspot detection after large scale disasters using location data from smartphones: case study of Kumamoto earthquake \cite {Yabe:2016:FEH:2996913.2997014} :
